\chapter{Conclusion and Future Work}
\minitoc

\section{Conclusion}

In conclusion, 
the development and deployment of a cutting-edge accelerated e-commerce deep learning recommendation system present both challenges and opportunities. 
Through the exploration of various recommendation system types, it is evident that DLRMs offer promising potential in terms of scalability and performance.
However, evaluation of the retrieval component reveals that the current Two-Tower model requires further optimization or replacement to enhance the selection of relevant items from vast product databases.
 Additionally, the system's latency increases with the number of items retrieved, indicating a need for improvements in the feature retrieval process.

 Moving forward, research will prioritize optimizing the retrieval stage, focusing on improving accuracy (especially recall) and reducing latency.
  A more effective retrieval model helps significantly in enhancing the user experience by presenting more relevant product recommendations, 
  leading to increased customer engagement and potentially higher sales. Furthermore, by addressing latency issues, the system can better handle real-time recommendation requests, ensuring a seamless browsing experience for e-commerce users. 
 Such optimizations have the potential to not only improve the performance of the systems but also contribute to advancements in the field of e-commerce personalization.

\section{Future Technical Work}
Build and implement the system's components, deploy and automate the recommendation pipeline and required infrastructure 
In addition to optimizing the ranking and retrieval models
There are many possible improvements and future work that can be done to the system, 
some of them are related to the model and data, and others are related to the system architecture and infrastructure.

The following sections will discuss some of the possible future work and improvements that can be made to improve the system.

\subsection{Deeper Product Features}

One of the main limitations of the current system is the lack of product features related to the product's content, such as the product's description, title, and images.
Adding these features to the model can improve the recommendation system's accuracy and performance. 
But to do that, the system needs to be able to process and analyze the product's content, which requires additional layers of data processing and feature extraction.

As an example, to extract features from the product's name and description, the system can use NLP
techniques to extract embeddings representing the product's content, and then use these embeddings as input features to the model.

For images, the system can use computer vision techniques, such as convolutional networks, to extract features from the product's images, and then use these features as input to the model.

\subsection{Increasing Interactions Data}

The current system recommends products solely based on a single type of interaction, which is the user's click history.
Adding more types of interactions, such as the user's purchase history, the user's rating history, and the user's browsing history, 
might improve the recommendation system's accuracy and performance.

Moreover, some interaction types might be converted to numeric features for further analysis,
 for example, a user opens the product page, and stays for a certain amount of time, 
 that time can be used as a feature to represent the user's interest in the product.

 \subsection{Integrating with Ecommerce Platforms}

The current system is a standalone system that provides an API for the client to interact with.
To make the system more accessible and easier to use, it can be integrated with popular e-commerce platforms, such as Shopify, Magento, and WooCommerce.
Such integration can be done by providing plugins or extensions that can be installed on the e-commerce platform, 
and then the plugin can communicate with the system's API to get recommendations for the platform's users.

\subsection{Session-based Recommendations}

The current system requires re-training to update the model with new data, and it does not take into account the user's current session or context.
So the customer's interactions do not affect the recommendations until the next re-training cycle.

A major improvement to the system is to add a session-based recommendation model that can provide real-time recommendations based on the user's current session and context.
Such a model can utilize RNN with LSTM to capture the user's session and context without requiring prior knowledge of the interactions during training. 

One possible library to use for this purpose is Merlin Transformer4Rec~\cite{NvidiaMerlinTransformers4Rec}, 
which is a flexible and efficient library for sequential and session-based recommendation~\cite{NvidiaMerlinTransformers4Rec}.


\section{Economic Implications On Silal}

This cutting-edge recommendation system, once optimized, holds immense potential to transform Silal's e-commerce businesses.
 By significantly improving the accuracy and relevance of product recommendations, it can drive increased customer engagement, higher click-through rates, and ultimately, increased sales. This translates to a direct boost in revenue for Silal. Additionally, the ability to provide real-time personalized recommendations can enhance the user experience, leading to improved customer satisfaction and loyalty, further contributing to long-term revenue growth. 

% The system can also be licensed or sold to other e-commerce businesses, generating additional revenue streams. 
% One potential model for revenue generation could involve taking a percentage of sales resulting from clicks on recommended items, providing a direct incentive to optimize the system's performance.
%  In essence, this project not only addresses a significant technological challenge but also opens doors to substantial economic opportunities in the world of online retail.